---
title: "Douglas_Tata"
author: "Tata"
date: "5/21/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# CIE76

The CIE76 deltaE was used in order to obtain an easy-to-calculate color measurement; the Euclidian distance is used for determining color distance.

using: 
$$ ({L_{1}^{*}},{a_{1}^{*}},{b_{1}^{*}})$$ and  $$({L_{2}^{*}},{a_{2}^{*}},{b_{2}^{*}}),$$ 
two colors in L*a*b*:

$$
\Delta E_{ab}^{*}={\sqrt {(L_{2}^{*}-L_{1}^{*})^{2}+(a_{2}^{*}-a_{1}^{*})^{2}+(b_{2}^{*}-b_{1}^{*})^{2}}}
$$

```{r load data, echo=FALSE}
# Load data
lab <- read.csv2("LabMeasurements-Color-Card.csv")
master <- read.csv2("MasterColorCard.csv")
```
```{r compute CIE76}
deltae <- matrix(NA,nrow = 546, ncol=66, byrow = TRUE)
deltae[,1] <- lab[,1]; 
deltae[,2] <- lab[,2]; 

# colnames(deltae)
colnames(deltae) <- c("Row", "Column", c(11:18, 21:28, 31:38, 41:48, 51:58, 61:68, 71:78, 81:88))

distance_single <- {}
distance_row <- {}
for (i in 1:length(row.names(lab))) {
    cardmatrix <- matrix(lab[i,-c(1:2)],nrow=64,ncol=3,byrow=TRUE)
    colnames(cardmatrix) = c("L","a","b")
    for (j in 1:64) {
        cardmatrix[j,] -> matrixA
        master[j,] -> matrixB
        distance_single <- sqrt((matrixA$L - matrixB$L)^2 + (matrixA$a - matrixB$a)^2 + (matrixA$b - matrixB$b)^2)
        distance_row[j] <- distance_single
    }
    deltae[i,-c(1:2)] <- distance_row
}
```

```{r plot CIE76, echo=FALSE}
hist(deltae, breaks = 20, xlim = c(0,40), 
     main = paste("Histogram of" , 'CIE76'),
     ylim = NULL,
     xlab = '', ylab = '', col = 'blue',
     axes = FALSE, plot = TRUE, labels = FALSE)
```

The results data concerning CIE76 euclidean distance is still distinguishable to the human eye under controlled viewing conditions (JND,just noticeable difference), the metric varies between 0.05 units and 36.44 units.

# Just Noticeable Difference
```{r heatmap code, echo = FALSE}
deltae -> CIE76
colorMean <- apply(CIE76[,3:66],2,mean)
colors_jnd <- {}
for (i in c(1:64)) {
  x <- colorMean[i] 
  if (x < 1)                #  Unnoticable to the human eye
    colors_jnd[i] = 1
  else if (1 < x && x < 2)  # barely noticable
    colors_jnd[i] = 2
  else if (2 < x && x < 4)  # noticable difference on a keen eye
    colors_jnd[i] = 3
  else if (4 < x )          # clearly distinct
    colors_jnd[i] = 4
}

mean_matrix <- matrix(colors_jnd, nrow = 8, ncol= 8, byrow = TRUE, dimnames = NULL)
```
heatmap with col = heatmap()
```{r heatmap, echo= FALSE}
mean_heatmap <- heatmap(mean_matrix, Rowv=NA, Colv=NA, col = heat.colors(4, alpha=1), 
                       scale="column", margins=c(5,10))
```
heatmap with col = rainbow
```{r heatmap1, echo= FALSE}
mean_heatmap <- heatmap(mean_matrix, Rowv=NA, Colv=NA, col = rainbow(4, s = 1, v = 1, start = 0, end = max(1, 4 - 1)/4, alpha = 1), 
                       scale="column", margins=c(5,10))
```

heatmap with col = cm.colors
```{r heatmap2, echo= FALSE}
mean_heatmap <- heatmap(mean_matrix, Rowv=NA, Colv=NA, col = cm.colors(4,  alpha = 1), 
                       scale="column", margins=c(5,10))
```


